A Dearth of Young Stars and Planets in the Kepler Field

### 2024-06-04 paper/ms.tex
update ms

\section{Regarding The Preferred Rotation Period Catalog}
\label{app:reinhold23}

While we opted for our default stellar rotation periods to be those
reported by \citetalias{Santos_2019} and \citetalias{Santos_2021},
the more recent analysis by \citet{Reinhold2023} bears comment.  \citet{Reinhold2023} used a
similar selection function as \citetauthor{Santos_2021}, and
considered a novel period measurement approach based on gradients of
power spectra (GPS).
Their method likely provides greater completeness, due
to its greater sensitivity to signals that are only weakly periodic.
However,
 comparing 
overlapping stars from
\citet{McQuillan_2014}, \citetalias{Santos_2019},
\citetalias{Santos_2021}, and \citet{Reinhold2023} suggested that for
stellar signals that are strongly periodic, 
the GPS method is likely a factor of a few times less precise than 
the more traditional approaches (ACF, Lomb-Scargle, or wavelet
analysis).

@@

The (arbitrary) method used to construct the orange line in 
the lower panel of Figure~\ref{fig:stellarprops} was as follows.
The line is	defined as
the maximum of two numerically-determined functions, $f_0(T_{\rm eff})$ and $f_1(T_{\rm eff})$.
We defined $f_0$ by fitting an
$N^{\rm th}$-order polynomial to the stars with rotation periods for which $t_{\rm
	B20,iso}/(+\sigma_{t,{\rm B20,iso}})\approx 3$
and $T_{\rm eff}\in[3700,5900]$\,K, where
$t_{\rm B20,iso}$ was the isochronal age reported by
\citet{Berger_2020a_catalog}.  We let the order of the fit vary from
$N$=1 to 10, minimized the Bayesian Information Criterion,
and found $N$=6.  
By eye, this yielded a plausible locus for $T_{\rm eff}$$\lesssim$5300\,K.
However for F and G dwarfs, the resulting locus
allowed for stars that were ``too evolved''; the density of KOIs 
was anomalously low in this region of the $\log g$ vs.\ $T$$_{\rm eff}$ plane.
We therefore visually selected KOIs that appeared
to be near the main sequence -- i.e.~most of the yellow
points in Figure~\ref{fig:stellarprops} -- and used them to fit a separate
polynomial $f_1$ through a similar BIC-minimization procedure,
which yielded $N$=3.
This polynomial, $f_1$, is shown in very faint opacity in Figure~\ref{fig:stellarprops}.
The portion of the orange locus from $\approx$5300--6200\,K
is set as $f_1 + c$, for $c$ a constant offset that we defined to be
0.1\,dex above the ``KOI main sequence''.
The exact break-point in temperature is automatically set by ${\rm max}(f_0, f_1+c)$.
We do report rotation-based ages for stars
above this orange locus;
they are simply flagged as not being near the main sequence in the $\log g$ vs.~$T_{\rm eff}$ plane.

@@

Kepler~411, a $\approx$780$\pm$170\,Myr early K dwarf with three
transiting planets at 3.0, 7.8, and 58\,days, has a rare
architecture.  \citet{2019A&A...624A..15S} conducted a transiting
timing analysis of the system, confirming Kepler-411d and arguing for
the presence of a fourth non-transiting planet, Kepler-411e, based on
the TTVs seen in Kepler-411d and assuming that the system is nearly
coplanar.  Regarding the stellar age, \citet{2019A&A...624A..15S} used
the \citet{2007ApJ...669.1167B} relation and the measured rotation
period, which yielded an estimate of 212$\pm$31\,Myr.  However, the
star's temperature ($\approx$4900\,K) puts it in a regime where the
\citeauthor{2007ApJ...669.1167B} relation has been known to not fit
observations for a while
\citep[e.g.][Fig.~9]{Mamajek_2008}.  Our adopted age of
$\approx$780$\pm$170\,Myr agrees with the open cluster calibrators.

>>>>

\section{The Preferred Rotation Period Catalog}
\label{app:reinhold23}

While we opted for the 
\citetalias{Santos_2019} and \citetalias{Santos_2021}
rotation period catalogs,
the more recent analysis by \citet{Reinhold2023} bears comment.  \citet{Reinhold2023} used a
similar selection function as \citeauthor{Santos_2021}, and
considered a novel period measurement approach based on gradients of
power spectra (GPS).
Their method likely provides greater completeness, due
to its greater sensitivity to signals that are only weakly periodic.
However,
 comparing 
overlapping stars from
\citet{McQuillan_2014}, \citetalias{Santos_2019},
\citetalias{Santos_2021}, and \citet{Reinhold2023} suggested that for
stellar signals that are strongly periodic, 
the GPS method is a few times less precise than 
the more traditional approaches (ACF, Lomb-Scargle, or wavelet
analysis).

@@

The (arbitrary) method used to construct the orange line in 
the lower panel of Figure~\ref{fig:stellarprops} was as follows.
The line is	defined as
the maximum of two numerically-determined functions, $f_0(T_{\rm eff})$ and $f_1(T_{\rm eff})$.
We defined $f_0$ by fitting an
$N^{\rm th}$-order polynomial to the stars with rotation periods for which $t_{\rm
	B20,iso}/(+\sigma_{t,{\rm B20,iso}})\approx 3$
and $T_{\rm eff}\in[3700,5900]$\,K, where
$t_{\rm B20,iso}$ was the isochronal age reported by
\citet{Berger_2020a_catalog}.  We let the order of the fit vary from
$N$=1 to 10, minimized the Bayesian Information Criterion,
and found $N$=6.  
By eye, this yielded a plausible locus for $T_{\rm eff}$$\lesssim$5300\,K.
However for F and G dwarfs, the resulting locus
allowed for stars that were ``too evolved''; the density of KOIs 
was anomalously low in this region of the $\log g$ vs.\ $T$$_{\rm eff}$ plane.
We therefore visually selected KOIs that appeared
to be near the main sequence -- i.e.~most of the yellow
points in Figure~\ref{fig:stellarprops} -- and used them to fit a separate
polynomial $f_1$ through a similar BIC-minimization procedure,
which yielded $N$=3.
This polynomial, $f_1$, is shown in very faint opacity in Figure~\ref{fig:stellarprops}.
The portion of the orange locus from $\approx$5300--6200\,K
is set as $f_1 + c$, for $c$ a constant offset that we defined to be
0.1\,dex above the ``KOI main sequence''.
The exact break-point in temperature is automatically set by ${\rm max}(f_0, f_1+c)$.
While we do report rotation-based ages for stars
above this orange locus,
they are flagged as not being near the main sequence in the $\log g$ vs.~$T_{\rm eff}$ plane.

@@

Kepler~411, a $t_{\rm gyro}$$\approx$780$\pm$170\,Myr early K dwarf with three
transiting planets at 3.0, 7.8, and 58\,days, has a rare
architecture.  \citet{2019A&A...624A..15S} conducted a transiting
timing analysis of the system, confirming Kepler-411d and arguing for
the presence of a fourth non-transiting planet, Kepler-411e, based on
the TTVs seen in Kepler-411d and assuming that the system is nearly
coplanar.  Regarding the stellar age, \citet{2019A&A...624A..15S} used
the \citet{2007ApJ...669.1167B} relation and the measured rotation
period, which yielded an estimate of 212$\pm$31\,Myr.  However, the
star's temperature ($\approx$4900\,K) puts it in a regime where the
\citeauthor{2007ApJ...669.1167B} relation has been known to not fit
observations for a while
\citep[e.g.][Fig.~9]{Mamajek_2008}.  Our adopted age of
$\approx$780$\pm$170\,Myr agrees with the open cluster calibrators.
